Example of Glenmore Reservoir Water Flow
========================================================

This is a hypothetical example with MANY assumptions of how the glenmore reservoir system will respond to precipitation.

**Disclaimer:** I'm not a hydrogeologist, and don't have any knowledge of how the systme actually works.

Here are some numbers about the Glenmore Reservoir:
```{r}
catchment.area<-1210*1000^2 #1,210km^2
surface.area<-3.84*1000^2 #3.84km^2
avg.depth<-6.1 # 6.1m average depth
max.depth<-21.1 # 21.1m max depth
```


If we then calculate the volumetric capacity of the reservoir assuming the average depth & surface area:
```{r}
capacity.avg<-surface.area*avg.depth 
capacity.avg
```

Now let's assume rain falls into the catchment area:
```{r}
precip.depth<-0.070 # 70mm average precipitation over catchment area
precip.volume<-catchment.area*precip.depth
precip.volume
```

Next let's use max out-flow of the Elbow River assumed to be ~ 600m3/s, to see how long it would take to dissipate
thus precipitation from Glenmore Reservoir:
```{r}
max.elbow<-600 #m3/s
dissipation.time<-precip.volume/(max.elbow*3600)
dissipation.time
```

If we're lucky, we might have some extra 'storage' capacity available in the reservoir. Let's assume the surface area
doesn't change (for simplicity), and we have the ability to add ~ 5m of water level into the reservoir:
```{r}
water.level.capacity<-5
spare.capacity<-surface.area*water.level.capacity
spare.capacity
```

Next let's suppose inflow from the Elbow is occurring at 500m3/s, and we can flow 200m3/s without downstream flooding:
```{r}
reservoir.inflow<-500 #m3/s
reservoir.outflow<-200 #m3/s, assume
fill.time<-spare.capacity/((reservoir.inflow-reservoir.outflow)*3600)
fill.time
```
So it would take ~ `r round(fill.time,0)` hours to fill that spare capacity, after this, we would have to increase flow down the Elbow river from the Glenmore Dam... 

There's a whole bunch of transient analysis that could be done to show the complexity of the system, but I'll leave that for the pros!
